---
title       : Image Classification
subtitle    : Model evaluation
author      : Andrey
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Project description

Classification model was created to classify images - bad/good automatically. 
<br><br>
This application helps to assess model performance. It contains results of 405 models. First result is based on 2 images in training set and next results gets by incrementing number of images by 1.
<br><br>
Final model result based on 406 images in training set.


--- .class #id 

## Performance Metrics of final model

```{r, echo = FALSE, render=FALSE}
# Home dir
main.dir <- "G:/_R/Image Classification/shiny"

# Data SubDir
data.dir <- "data"

# Results file name
results.file <- "Results.RData"

# Model performance file name
perf.file <- "Perf.RData"

# Load data
Results <- readRDS(file.path(main.dir, data.dir, results.file))
Perf <- readRDS(file.path(main.dir, data.dir, perf.file))

library(shiny)
library(ggplot2)
library(dplyr)
```        


```{r, echo = FALSE}

cat('Accuracy: ', Results$accuracy.test[405])
cat('TP: ', Results$TP[405], ' FP: ', Results$FP[405], ' FN: ', Results$FN[405], ' TN: ',  Results$TN[405], '\n')
cat('Precision: ', round(Results$precision[405], 4), ' Recall: ', round(Results$recall[405], 4), ' F1 Score: ', round(Results$F1[405], 4), '\n')


```   

--- .class #id 

## Learning curves

By plotting learning curves we can assess how does the accuracy of a learning method change as a function of the training set size

```{r, echo = FALSE}
    
                        g <- ggplot(Results, aes(x=N))
                        g <- g + geom_line(aes(y=accuracy.test), size = 0.5, color = "blue")
                        g <- g + geom_line(aes(y=accuracy.train), size = 0.5, color = "blue")
                        g <- g + geom_smooth(aes(y=accuracy.test), size = 1, method = "lm",  color = "blue")
                        g <- g + geom_point(aes(y=accuracy.train), color = "blue")
                        g <- g + geom_point(aes(y=accuracy.test), color = "blue")
                        g <- g + theme_bw()
                        g <- g + coord_fixed(ratio = 600)
                        g <- g + theme(plot.title = element_text(size = rel(2)))
                        g <- g + theme(axis.text = element_text(size = rel(1)))
                        g <- g + theme(axis.title = element_text(size = rel(2)))
                        g <- g + xlab("Size of the Training set")
                        g <- g + ylab("Accuracy")
                        g <- g + ggtitle("Learning Curves")
                        g

```   

--- .class #id 

## Summary

This plot is showing absolute difference Good and Bad probabilities. If it small them we can conclude that model not sure about whcih class should be for that image.
<br><br>
Additionally we can see which images was classified incorrectly as False Positives (FP) and False Negatives (FN)

```{r, echo = FALSE}
                        g <- ggplot(filter(Perf, iter == 405), aes(x = as.factor(img.num), y = Diff))
                        g <- g + geom_bar(aes(fill = Type), stat = 'identity', colour = 'black')
                        g <- g + scale_fill_manual(values=c("maroon", "red", "green", "lightgreen"))
                        g <- g + scale_y_sqrt()
                        g <- g + theme_bw()
                        g <- g + theme(plot.title = element_text(size = rel(2)))
                        g <- g + theme(axis.text = element_text(size = rel(1)))
                        g <- g + theme(axis.title = element_text(size = rel(1)))
                        g <- g + xlab("Images from the Testing set")
                        g <- g + ylab("Difference = Absolute(Prob Good - Prob Bad)")
                        g <- g + ggtitle("Show image difference")
                        g <- g + coord_fixed(ratio = 50)
                        g



```        



